Data Specialization for a Staged Lambda Calculus

### 2014-11-09 paper/splitting.tex
BUGFIX: fixed error in resumer in Stage-2 splitting.
Small cleanup in 4.2 and 4.3 to be consistent with terminology.

Splitting a stage~\bbone\ term $e$ in \lang\ yields a term 
$e_1$ that performs all stage~\bbone\ subcomputations in $e$ and a \emph{resumer} function $e_2 = l.r$ that performs all stage~\bbtwo\ subcomputations.
To ensure that the results of splitting produce the same output as the evaluation $e\mathbin{\redonesym}[\xi;v]$,
we require that $e_1$ reduce to the tuple $(y,b)$,
where $y$ is identical to $\masko{\xi;v}$, and 
$\letin l b r$ reduces to the same value as $\maskt{\xi;v}$. Since~$e_1$ performs both stage~\bbone\ subcomputations needed to produce $y$ (a value we call the \emph{stage~\bbone\ result}), and the stage~\bbone\ subcomputations (called \emph{precomputations}) that produce the \emph{boundary value} $b$ required by the resumer, we refer to this term as the \emph{combined term}, and hereafter denote it as $c$.

@@

Because stage~\bbtwo\ terms in \lang\ fully reduce to values (as opposed to partial values),
splitting stage~\bbtwo\ terms in \lang\ assumes a simpler form than that of stage~\bbone\ term splitting. 
Specifically, splitting a stage~\bbtwo\ term $e$ in \lang\ generates a precomputation term $p$
(performing all stage~\bbone\ subcomputations in $e$) and a
resumer function $e_2=l.r$ (performing all stage~\bbtwo\ subcomputations) such that when 
$e$ reduces to the value~$v$, $\letin l p r$ reduces to an identical value in \langmono.
Note that in contrast to the combined term produced during stage~\bbone\ splitting,
the precomputation $p$ generated by stage~\bbtwo\ splitting exists entirely
to compute the input expected by the resumer.

>>>>

Splitting a stage~\bbone\ term $e$ in \lang\ yields a term 
$e_1$ that performs all stage~\bbone\ subcomputations in $e$ and a \emph{resumer term} $e_2 = l.r$ that performs all stage~\bbtwo\ subcomputations.
To ensure the results of splitting produce the same output as the evaluation $e\mathbin{\redonesym}[\xi;v]$,
we require that $e_1$ reduce to the tuple $(y,b)$,
where $y$, called the \emph{\bbone-result} of $e$, is identical to $\masko{\xi;v}$, and that
$\letin l b r$ reduces to the same value as $\maskt{\xi;v}$. (We refer to $b$ as the \emph{boundary value} of the split since it carries information between stage~\bbone\ and stage~\bbtwo\ subcomputations.) Since~$e_1$ performs both stage~\bbone\ subcomputations needed to produce the \bbone-result and subcomputations (refered to as \emph{precomputations}) that produce the boundary value, we refer to this term as the \emph{combined term}, and hereafter denote it as~$c$.

@@

Because stage~\bbtwo\ terms in \lang\ fully reduce to values (as opposed to partial values),
splitting stage~\bbtwo\ terms in \lang\ assumes a simpler form than that of stage~\bbone\ term splitting. 
Specifically, splitting a stage~\bbtwo\ term $e$ in \lang\ generates a precomputation term $p$
(performing all stage~\bbone\ subcomputations in $e$) and a
resumer term $e_2=l.r$ (performing all stage~\bbtwo\ subcomputations) such that when 
$e$ reduces to the value~$v$, $\letin l p r$ reduces to an identical value in \langmono.
Note that in contrast to the combined term produced during stage~\bbone\ splitting,
the precomputation $p$ generated by stage~\bbtwo\ splitting exists entirely
to compute the boundary value expected by the resumer.
